Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
updated based on changes made to repository

- Remove NAs from test data
- Update readme after file changes (and practice making new submission folder, maybe create a script for copying the files)
- Finish filling in questions in ASA submission document
- Write cover letter
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

@@

- information about the files in the repository,
- instructions for knitting the paper,
- descriptions of the bullet data used in the paper, 
- information on the font sizes used for the figures in the manuscript, and
- the steps taken to create the `submission` folder.

@@

Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):

- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

@@

Contains the data used to generate the manuscript:

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.

@@

Contains the static figure associated with the project:

- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.

@@

Contains the files submitted to the ASA data science journal. These files are moved to this folder using code in the file `code/file-organization.R`.

**Files**

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output. :)
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

@@

1. Pull the repository from GitHub.
2. Install R packages goodekat/lime and goodekat/limeaid from GitHub using the remotes R package. (Note that goodekat/lime is a forked versions of thomasp85/lime with minor changes to extract objects for the analysis in the manuscript.)

@@

The data used in the manuscript for the bullet comparison examples is described below.

@@

The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures. The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below. Note that the text in the manuscript is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.

@@

## Steps Followed to Create the Submission Folder

Follow these steps to make sure all guidelines are met for submission.

1. Knit the file `paper.Rnw` (to make sure everything is up to date).
2. Run the code in the file `code-file-organization.R` for producing an R script with all of the code from the manuscript (paper.Rnw).
3. Move the following files to the `submission` folder:
    - `code-paper.R`
    - `data-bullet-test.csv`
    - `data-bullet-train.csv`
    - `data-example-signatures.csv`
    - `figure/figure-XX-1.eps` (for XX = 01-07, 09, 11-13, B1, B2, and C3)
    - `figure-08-1.eps`
    - `figure-10-1.eps`
    - `paper.tex`
    - `readme.txt`
    - `references.bib`
    - `WileyNJD-AMS.bst`
    - `WileyNJD-v1.csl`
4. Change the name of `paper.tex` to `paper-submission.tex`.
5. Delete `figure/` from the figure file paths in `paper-submission.tex`. For example, change \includegraphics[width=6.5in]{figure/figure-01-1} to \includegraphics[width=6.5in]{figure-01-1}.
6. Compile the file `paper-submission.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly. 
7. Besides for `paper-submission.pdf`, delete all other files generated when `paper-sumbission.tex` was compiled. This includes other `paper-submission` files and pdf versions of the figures.
8. Convert the following files in the submission folder to a zip file, call it `code-and-data.zip`, and then delete the unzipped versions of the files:
    - `code-paper.R`
    - `data-bullet-test.csv`
    - `data-bullet-train.csv`
    - `data-example-signatures.csv`
    - `readme.txt`
9. Upload all remaining files to ASA data science journal submission page (except for `paper-submission.Rnw`) which should be:
    - `code-and-data.zip`
    - `figure-01-1.eps` through `figure-C3-1.eps`
    - `paper-sumbission.pdf`
    - `paper-sumbission.tex`
    - `references.bib`
    - `WileyNJD-AMS.bst`
    - `WileyNJD-v2.cls`

>>>>

- Remove NAs from test data
- Write cover letter
- Finish filling in questions in ASA submission document
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

@@

- information about the files in the repository,
- instructions for knitting the paper,
- descriptions of the bullet data used in the paper, and
- information on the font sizes used for the figures in the paper.

@@

Contains the R code associated with the paper that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):

- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
- `figure-compression.R` contains R code for compressing the static figure used in the paper
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

@@

Contains the data used to generate the paper:

- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper. Additional information about these files is included below under the heading "Additional Information on Bullet Data".
- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
- `raw` contains the raw versions of the data files that the above datasets are derived from.

@@

Contains the static figures associated with the project:

- `figure-08-1.png.zip` is the one figure in the paper that is not generated using R code.
- `figure-readme.png` is a figure used in the readme.

@@

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file `code/submission-steps.R`. The only figures not included on GitHub are the EPS figures that are submitted due to size constraints.

**Main Directory**

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the paper. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
- `README.Rmd` and `README.md` are the readme files that generated this output.
- `readme.txt` contains descriptions of the data files that are included with the submission
- `references.bib` contains the bibtex information for the references in the paper
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.

@@

1. Pull the repository from GitHub.
2. Install R packages [goodekat/lime](https://github.com/goodekat/lime) and [goodekat/limeaid](https://github.com/goodekat/limeaid) from GitHub using the remotes R package. (Note that goodekat/lime is a forked versions of [thomasp85/lime](https://github.com/thomasp85/lime) with minor changes to extract objects for the analysis in the paper.)

@@

The data used in the paper for the bullet comparison examples is described below.

@@

The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures. The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below. Note that the text in the paper is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.

@@
